Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-03-16 TEBenchmarkPaper/article.tex
Acknowledgements

%\begin{acknowledgements}
%  EPSRC
%\end{acknowledgements}

>>>>

\begin{acknowledgements}
  We are grateful to the authors of the systems we have used in our experiments,
  especially for help in obtaining and configuring their tools. We would
  especially like to thank Koen Claessen, Lucas Dixon, Moa Johansson, Dan
  Ros\'{e}n and Nicholas Smallbone for useful discussions and help in adapting
  their software to our purposes.
%  EPSRC
\end{acknowledgements}
